String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-10-20 2023-1-19/crv/sections/cefa.tex
add crv folder

%!TEX root = ../main.tex
In this section, we define the cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
%
Intuitively, CEFA adds write-only cost registers to finite state automata. ``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions. 
%
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
  \begin{itemize}
  \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
    \item $Q, \Sigma, I, F$ are as in the definition of NFA,
    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
    \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
  \end{itemize}
\end{definition}

@@

In the sequel, we define three CEFA operations: union, intersection, and concatenation. The following section will use these three operations to solve RECL constraints. Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the technical choice that the accepting condition is attached to each automaton, not each final state.

>>>>

%!TEX root = ../main.tex
In this section, we define cost-enriched finite state automata (CEFA), which was introduced in \cite{atva2020} and will be used to solve the satisfiability problem of RECL later on. 
%
Intuitively, CEFA adds write-only cost registers to finite state automata. ``write-only'' means that the cost registers can only be written/updated but cannot be read, i.e., they cannot be used to guard the transitions. 
%
\begin{definition}[Cost-Enriched Finite Automaton]
  A cost-enriched finite automaton $\aut$ is a tuple $(R, Q, \Sigma, \delta, I, F, \alpha)$ where
  \begin{itemize}
  \item $R = \{r_1, \cdots, r_k\}$ is a finite set of registers, 
    \item $Q, \Sigma, I, F$ are as in the definition of NFA,
    \item $\delta \subseteq Q \times \Sigma \times Q \times \Int^R$ is a transition relation, where $\Int^R$ denotes the updates on the values of registers.
    \item $\alpha \in \Phi(R)$ is an LIA formula specifying an accepting condition.
  \end{itemize}
\end{definition}

@@

In the sequel, we define three CEFA operations: union, intersection, and concatenation. The following section will use these three operations to solve RECL constraints. Note that the union, intersection, and concatenation operations are defined in a slightly more involved manner than register automata~\cite{ra} and counter automata~\cite{GGM12}, as a result of the (additional) accepting conditions. 
%the technical choice that the accepting condition is attached to each automaton, not to each final state.
